Causal Impact of Masks, Policies, Behavior on Early Covid-19 Pandemic in the U.S.

### 2020-07-29 cases_and_policies/rmd/regressionsWithPlots.Rmd
update on us governor party
(i) add republican party dummy to state-level characteristics
(ii) change robustness table

```{r caseregs, cache=FALSE, warning=FALSE, results='hide'}
infovars <- list(c("dlogdc", "logdc"),
                 c("dlogdc", "logdc","dlogdc.national", "logdc.national")) #,
#c("dlogdc", "logdc"))
#infovars2 <- list(c( "logdc"))
tvars <- "dlogtests"  
xlist <-list("", "") 
interactions <-list("month", statevars)
ilist <- list(interactions, interactions)
iv <- list("0","0") #,"(testratedc ~ lag(testratedc,14))")

@@

L <- 14
sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L)
piy <- list()
yvar <- "dlogdc"
for (k in 1:length(infovars)) {
  # (1) excluding NY 
   xlist <-list("","")
  sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L) 
  sdf2 <- sdf[which(sdf$state!='New York'),]
  piy[[(1+4*(k-1))]] <- policyreg(sdf2, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", infovars[[k]], L),
                tvars, xlist[[k]]),
              ilist[[k]], 0, L=L)
  # (2) adding mask wearing rate and log(Trump's vote)
  sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L)
  xlist <-list(c("z.mask","logvote"), c("z.mask","logvote"))
  piy[[(2+4*(k-1))]] <- policyreg(sdf, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", infovars[[k]], L),
                tvars, xlist[[k]]),
              ilist[[k]], 0, L=L)
  # (3) lagged behavior variables
  sdf <- subset(df, df$date>=as.Date("2020-02-22")) #+L)
  xlist <-list("","")
  piy[[(3+4*(k-1))]] <- policyreg(sdf, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", bvars, L+14),
                sprintf("lag(%s, %d)", infovars[[k]], L),
                tvars, xlist[[k]]),
              ilist[[k]], 0, L=L)
  # (4) (1)-(3)
   sdf <- subset(df, df$date>=as.Date("2020-02-22")) #+L) 
   sdf2 <- sdf[which(sdf$state!='New York'),]
   xlist <-list(c("z.mask","logvote"), c("z.mask","logvote"))
   piy[[(4+4*(k-1))]] <- policyreg(sdf2, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", bvars, L+14),
                sprintf("lag(%s, %d)", infovars[[k]], L),
                tvars, xlist[[k]]),
              ilist[[k]], 0, L=L)

}

@@

L <- 21
sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L)
piy <- list()
yvar <- "dlogdd"
infovars <- list(c("dlogdd", "logdd"),
                  c("dlogdd", "logdd","dlogdd.national", "logdd.national"))
#xlist <-list(c("z.mask","logvote"), c("z.mask","logvote"))
for (k in 1:length(infovars)) {
  # (1) excluding NY 
  xlist <-list("","")
  sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L) 
  sdf2 <- sdf[which(sdf$state!='New York'),]
  piy[[(1+4*(k-1))]] <- policyreg(sdf2, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", infovars[[k]], L),
                 xlist[[k]]),
              ilist[[k]], 0, L=L)
  # (2) adding mask wearing rate and log(Trump's vote)
  sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L)
  xlist <-list(c("z.mask","logvote"), c("z.mask","logvote"))
  piy[[(2+4*(k-1))]] <- policyreg(sdf, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", infovars[[k]], L),
                 xlist[[k]]),
              ilist[[k]], 0, L=L)
  # (3) lagged behavior variables
  sdf <- subset(df, df$date>=as.Date("2020-02-22")) #+L)
  xlist <-list("","")
  piy[[(3+4*(k-1))]] <- policyreg(sdf, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", bvars, L+14),
                sprintf("lag(%s, %d)", infovars[[k]], L),
                 xlist[[k]]),
              ilist[[k]], 0, L=L)
  # (4) (1)-(3)
   sdf <- subset(df, df$date>=as.Date("2020-02-22")) #+L)
   # sdf2 <- sdf[which(sdf$state!='New York' & sdf$state!='New Jersey' & sdf$state!='Connecticut' & sdf$state!='Massachusetts'),]
   sdf2 <- sdf[which(sdf$state!='New York'),]
   xlist <-list(c("z.mask","logvote"), c("z.mask","logvote"))
   piy[[(4+4*(k-1))]] <- policyreg(sdf2, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", bvars, L+14),
                sprintf("lag(%s, %d)", infovars[[k]], L),
                xlist[[k]]),
              ilist[[k]], 0, L=L)

>>>>

```{r caseregs, cache=FALSE, warning=FALSE, results='hide'}
infovars <- list(c("dlogdc", "logdc"),
                 c("dlogdc", "logdc","dlogdc.national", "logdc.national")) #,
#c("dlogdc", "logdc"))
#infovars2 <- list(c( "logdc"))
tvars <- "dlogtests"  
# xlist <-list("party", "party") 
xlist <-list(c("party","logvote"), c("party","logvote")) 
interactions <-list("month", statevars)
ilist <- list(interactions, interactions)
iv <- list("0","0") #,"(testratedc ~ lag(testratedc,14))")

@@

L <- 14
sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L)
piy <- list()
yvar <- "dlogdc"
for (k in 1:length(infovars)) {
  # (1) excluding NY 
   xlist <-list("","")
  sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L) 
  sdf2 <- sdf[which(sdf$state!='New York'),]
  piy[[(1+5*(k-1))]] <- policyreg(sdf2, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", infovars[[k]], L),
                tvars, xlist[[k]]),
              ilist[[k]], 0, L=L)
  # (2) adding mask wearing rate  
  sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L)
  xlist <-list(c("z.mask"), c("z.mask"))
  piy[[(2+5*(k-1))]] <- policyreg(sdf, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", infovars[[k]], L),
                tvars, xlist[[k]]),
              ilist[[k]], 0, L=L)
  # (2) adding log(Trump's vote)
  sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L)
  xlist <-list(c("logvote","party"), c("logvote","party"))
  piy[[(3+5*(k-1))]] <- policyreg(sdf, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", infovars[[k]], L),
                tvars, xlist[[k]]),
              ilist[[k]], 0, L=L)
  # (4) lagged behavior variables
  sdf <- subset(df, df$date>=as.Date("2020-02-22")) #+L)
  xlist <-list("","")
  piy[[(4+5*(k-1))]] <- policyreg(sdf, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", bvars, L+14),
                sprintf("lag(%s, %d)", infovars[[k]], L),
                tvars, xlist[[k]]),
              ilist[[k]], 0, L=L)
  # (5) (1)-(4)
   sdf <- subset(df, df$date>=as.Date("2020-02-22")) #+L) 
   sdf2 <- sdf[which(sdf$state!='New York'),]
  xlist <-list(c("z.mask","logvote","party"), c("z.mask","logvote","party"))
   piy[[(5+5*(k-1))]] <- policyreg(sdf2, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", bvars, L+14),
                sprintf("lag(%s, %d)", infovars[[k]], L),
                tvars, xlist[[k]]),
              ilist[[k]], 0, L=L)
}

@@

L <- 21
sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L)
piy <- list()
yvar <- "dlogdd"
infovars <- list(c("dlogdd", "logdd"),
                  c("dlogdd", "logdd","dlogdd.national", "logdd.national"))
#xlist <-list(c("z.mask","logvote"), c("z.mask","logvote"))
for (k in 1:length(infovars)) {
  # (1) excluding NY 
  xlist <-list("","")
  sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L) 
  sdf2 <- sdf[which(sdf$state!='New York'),]
  piy[[(1+5*(k-1))]] <- policyreg(sdf2, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", infovars[[k]], L),
                 xlist[[k]]),
              ilist[[k]], 0, L=L)
  # (2) adding mask wearing rate 
  sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L)
  xlist <-list(c("z.mask"), c("z.mask"))
  piy[[(2+5*(k-1))]] <- policyreg(sdf, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", infovars[[k]], L),
                 xlist[[k]]),
              ilist[[k]], 0, L=L)
  # (3) adding log(Trump's vote)
  sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L)
  xlist <-list(c("logvote"), c("logvote"))
  piy[[(3+5*(k-1))]] <- policyreg(sdf, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", infovars[[k]], L),
                 xlist[[k]]),
              ilist[[k]], 0, L=L)
  # (4) lagged behavior variables
  sdf <- subset(df, df$date>=as.Date("2020-02-22")) #+L)
  xlist <-list("","")
  piy[[(4+5*(k-1))]] <- policyreg(sdf, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", bvars, L+14),
                sprintf("lag(%s, %d)", infovars[[k]], L),
                 xlist[[k]]),
              ilist[[k]], 0, L=L)
  # (5) (1)-(4)
   sdf <- subset(df, df$date>=as.Date("2020-02-22")) #+L)
   # sdf2 <- sdf[which(sdf$state!='New York' & sdf$state!='New Jersey' & sdf$state!='Connecticut' & sdf$state!='Massachusetts'),]
   sdf2 <- sdf[which(sdf$state!='New York'),]
   xlist <-list(c("z.mask","logvote"), c("z.mask","logvote"))
   piy[[(5+5*(k-1))]] <- policyreg(sdf2, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", bvars, L+14),
                sprintf("lag(%s, %d)", infovars[[k]], L),
                xlist[[k]]),
              ilist[[k]], 0, L=L)

### 2020-07-29 tex/tables_and_figures/policies.tex
update
update on us governor party
(i) add republican party dummy to state-level characteristics
(ii) change robustness table

% latex table generated in R 4.0.0 by xtable 1.8-4 package
% Sat Jul 25 16:38:15 2020
\begin{table}[ht]
\centering
\begin{tabular}{rllll}
  \hline
 & N & Min & Median & Max \\ 
  \hline
State of emergency & 50 & 2020-02-29 & 2020-03-11 & 2020-03-16 \\ 
  Date closed K 12 schools & 50 & 2020-03-13 & 2020-03-17 & 2020-04-03 \\ 
  Closed day cares & 14 & 2020-03-16 & 2020-03-23 & 2020-04-06 \\ 
  Date banned visitors to nursing homes & 29 & 2020-03-09 & 2020-03-16 & 2020-04-06 \\ 
  Closed non essential businesses & 42 & 2020-03-19 & 2020-03-25 & 2020-04-06 \\ 
  Closed restaurants except take out & 47 & 2020-03-15 & 2020-03-17 & 2020-04-03 \\ 
  Closed gyms & 45 & 2020-03-16 & 2020-03-20 & 2020-04-03 \\ 
  Closed movie theaters & 48 & 2020-03-16 & 2020-03-20 & 2020-04-06 \\ 
  Stay at home  shelter in place & 41 & 2020-03-19 & 2020-03-28 & 2020-04-07 \\ 
  End relax stay at home shelter in place & 37 & 2020-04-24 & 2020-05-16 & 2020-06-19 \\ 
  Began to reopen businesses statewide & 49 & 2020-04-20 & 2020-05-07 & 2020-06-05 \\ 
  Reopen restaurants & 47 & 2020-04-24 & 2020-05-18 & 2020-06-22 \\ 
  Reopened gyms & 43 & 2020-04-24 & 2020-05-18 & 2020-07-03 \\ 
  Reopened movie theaters & 36 & 2020-04-27 & 2020-05-31 & 2020-07-03 \\ 
  Resumed elective medical procedures & 34 & 2020-04-20 & 2020-04-29 & 2020-05-29 \\ 
  Mandate face mask use by all individuals in public spaces & 31 & 2020-04-08 & 2020-06-18 & 2020-07-27 \\ 
  Mandate face mask use by employees in public facing businesses & 41 & 2020-04-03 & 2020-05-01 & 2020-07-03 \\ 
  Stop Initiation of Evictions overall or due to COVID related issues & 29 & 2020-03-16 & 2020-03-24 & 2020-05-30 \\ 
  Stop enforcement of evictions overall or due to COVID related issues & 28 & 2020-03-15 & 2020-03-24 & 2020-06-08 \\ 
  Renter grace period or use of security deposit to pay rent & 3 & 2020-04-10 & 2020-04-24 & 2020-05-20 \\ 
  Order freezing utility shut offs & 33 & 2020-03-12 & 2020-03-19 & 2020-04-13 \\ 
  Froze mortgage payments & 1 & 2020-03-21 & 2020-03-21 & 2020-03-21 \\ 
  Waived one week waiting period for unemployment insurance & 35 & 2020-03-08 & 2020-03-18 & 2020-04-06 \\ 
   \hline
\end{tabular}
\caption{State Policies \label{tab:policies}} 
\end{table}

>>>>

% latex table generated in R 4.0.0 by xtable 1.8-4 package
% Wed Jul 29 09:27:24 2020
\begin{table}[ht]
\centering
\begin{tabular}{rllll}
  \hline
 & N & Min & Median & Max \\ 
  \hline
State of emergency & 49 & 2020-02-29 & 2020-03-11 & 2020-03-16 \\ 
  Date closed K 12 schools & 49 & 2020-03-13 & 2020-03-17 & 2020-04-03 \\ 
  Closed day cares & 14 & 2020-03-16 & 2020-03-23 & 2020-04-06 \\ 
  Date banned visitors to nursing homes & 29 & 2020-03-09 & 2020-03-16 & 2020-04-06 \\ 
  Closed non essential businesses & 41 & 2020-03-19 & 2020-03-25 & 2020-04-06 \\ 
  Closed restaurants except take out & 46 & 2020-03-15 & 2020-03-17 & 2020-04-03 \\ 
  Closed gyms & 44 & 2020-03-16 & 2020-03-20 & 2020-04-03 \\ 
  Closed movie theaters & 47 & 2020-03-16 & 2020-03-21 & 2020-04-06 \\ 
  Stay at home  shelter in place & 40 & 2020-03-19 & 2020-03-28 & 2020-04-07 \\ 
  End relax stay at home shelter in place & 36 & 2020-04-24 & 2020-05-15 & 2020-06-19 \\ 
  Began to reopen businesses statewide & 48 & 2020-04-20 & 2020-05-06 & 2020-06-05 \\ 
  Reopen restaurants & 46 & 2020-04-24 & 2020-05-17 & 2020-06-22 \\ 
  Reopened gyms & 42 & 2020-04-24 & 2020-05-18 & 2020-07-03 \\ 
  Reopened movie theaters & 35 & 2020-04-27 & 2020-05-30 & 2020-07-03 \\ 
  Resumed elective medical procedures & 34 & 2020-04-20 & 2020-04-29 & 2020-05-29 \\ 
  Mandate face mask use by all individuals in public spaces & 30 & 2020-04-08 & 2020-06-22 & 2020-07-27 \\ 
  Mandate face mask use by employees in public facing businesses & 40 & 2020-04-03 & 2020-05-01 & 2020-07-03 \\ 
  Stop Initiation of Evictions overall or due to COVID related issues & 29 & 2020-03-16 & 2020-03-24 & 2020-05-30 \\ 
  Stop enforcement of evictions overall or due to COVID related issues & 27 & 2020-03-17 & 2020-03-24 & 2020-06-08 \\ 
  Renter grace period or use of security deposit to pay rent & 3 & 2020-04-10 & 2020-04-24 & 2020-05-20 \\ 
  Order freezing utility shut offs & 32 & 2020-03-12 & 2020-03-19 & 2020-04-13 \\ 
  Froze mortgage payments & 1 & 2020-03-21 & 2020-03-21 & 2020-03-21 \\ 
  Waived one week waiting period for unemployment insurance & 35 & 2020-03-08 & 2020-03-18 & 2020-04-06 \\ 
   \hline
\end{tabular}
\caption{State Policies \label{tab:policies}} 
\end{table}
